\Large\bf Paper Title\footnotetext{Diese Arbeit ist Bestandteil des Prokatikums zur Mess- und Regelungstechnik}

### 2017-09-02 latex/paper.tex
added email address
test

\author{Ihr name\\
  Robotik und Telematik \\
  Universität Würzburg\\
  Am Hubland, D-97074 Würzburg\\
{\small \texttt{\{your\_email@uni-wuerzburg.de}}}

>>>>

\author{Ihr name\\
  Robotik und Telematik \\
  Universität Würzburg\\
  Am Hubland, D-97074 Würzburg\\
{\small \texttt{barbara.fischbach@uni-wuerzburg.de}}\\
{\small \texttt{kai.hofmann@uni-wuerzburg.de}}}
